Wigglyhedra

### 2024-02-28 draft/wigglyhedra.tex
Half a proof.

\begin{proof}
%We first have to prove that~$\Phi$ and~$\Psi$ are well-defined.
\vincent{todo}
\end{proof}

>>>>

\begin{proof}
%We first have to prove that~$\Phi$ and~$\Psi$ are well-defined.
  \vincent{todo}
  Let us first prove that for any wiggly permutation \(\sigma\), the set \(\Psi(\sigma)\) is a wiggly pseudotriangulation.
  By~\cref{prop:wigglyPseudotriangulations}, it suffices to check that for each \(k \neq k'\) in \([2n-1]\), the arcs 
  \(\alpha(\sigma,k)\) and \(\alpha(\sigma,k')\) are distinct and compatible.
  First suppose that \(k \leq k'\) and \(\alpha(\sigma,k) = \alpha(\sigma,k') = (i,j,A,B)\).
  It is easy to see that for any \(l \in [n]\), we have \(2l \in \sigma([k']) \ssm \sigma([k])\) if and only if \(2l -1 \in \sigma([k']) \ssm \sigma([k])\).
  If \(2l \in \sigma([k']) \ssm \sigma([k])\); equivalently \(2l - 1 \in \sigma([k']) \ssm \sigma([k])\), it is easy to check that
  \[i < l < j.\]
  \asilata[inline]{Fix definitions to check distinctness.}
  We check compatibility.
  Suppose that
  \[\alpha(\sigma,k) = (i,j,A,B) \text{ and }\alpha(\sigma,k') = (i',j',A',B').\]
  It is clear from the definition that \(i \neq j'\), as the sets over which we take the max and min to define \(i\) and \(j'\) respectively are disjoint.
  Similarly, we have \(j \neq i'\).
  Therefore the two arcs are pointed.
  To check that the arcs are non-crossing, we must show that the sets
  \[(A \cap B') \cup (\{i,j\} \cap B') \cup (A \cap \{i',j'\}) \text{ and } (A' \cap B) \cup (\{i',j'\} \cap B) \cup (A' \cap \{i,j\})\]
  are both empty.
  We check the first; the second is similar.
  \asilata[inline]{Fix definitions to check non-crossing-ness.}

\end{proof}
